Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-11 manuscript/manuscript.Rmd
embedding tables

## Problem Description and Data

@@

@@

We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to 
match that of the target variable. Because the `flood_zone` variable in the original data contains 60 levels, we take 
the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
`"A02"`, and so on are recoded as simply `"A"`.

@@

A log link together with the gamma distribution is a standard choice for severity modeling, which provides a 
multiplicative structure where the response is positive.

@@

For Model 2, we build a feedforward neural network. The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being sent to a hidden linear layer of 16 units. A ReLU (TODO: reference an equation in prev. section) activation
is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
predictions to be positive, we apply softplus activation, which is defined to be

@@

Figure \@ref(fig:nn-1) exhibits the architecture of our simple neural network.

@@

>>>>

## Problem Description and Experiment Setup

@@

(talk about experiment setup -- we take a subset of data that's shared for all models, then for the CV performance
evaluation only we use all data in CV splits?)

@@

We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to 
match that of the target variable. Because the `flood_zone` variable in the original data contains 60 levels, we take 
the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
`"A02"`, and so on are recoded as simply `"A"`. A log link together with the gamma distribution is a standard choice 
for severity modeling, which provides a multiplicative structure where the response is positive.

@@

In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, 
of a couple categorical variables. Recall that the choice of the log link gives a multiplicative structure, so the
interpretation of 1.37 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected 
loss for
a policy for a non-residential building is 1.37 times that of a policy for a single family home, which is the base,
or reference, level for the factor.

Table: (\#tab:relativities) Excerpt of relativities for Model 1.

|variable       |label                                       | relativity|
|:--------------|:-------------------------------------------|----------:|
|occupancy_type |Single family residence                     |       1.00|
|occupancy_type |Non-residential building                    |       1.37|
|occupancy_type |2 to 4 unit residential buidling            |       1.15|
|occupancy_type |Residential building with more than 4 units |       1.64|
|flood_zone     |B                                           |       1.00|
|flood_zone     |A                                           |       0.84|
|flood_zone     |C                                           |       0.60|
|flood_zone     |X                                           |       0.70|
|flood_zone     |V                                           |       0.78|
|flood_zone     |D                                           |       0.89|

@@

For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1). 
The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units. A ReLU (TODO: reference an equation in prev. section) activation
is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
predictions to be positive, we apply softplus activation, which is defined to be

@@

@@

In Tables \@ref(tab:embeddings-occupancy-type) and \@ref(tab:embeddings-flood-zone), we show the learned embeddings
for the `occupancy_type` and an excerpt of them for `flood_zone`. While it may be tempting to compare these values
to those in Table \@ref(tab:relativities), they represent fundamentally different concepts. It is helpful to think
of the embedding values for each variable as a continuous represention of the variable itself, rather than a 
"coefficient" associated with the variable. Note that it is not straightforward to inspect the embeddings from a
table and infer relationships to the response variable, even in a shallow network such as ours, due to nonlinearities
within the model. Also note that we now have a way to incorporate the full granularity of the `flood_zone` variable,
which is why more levels are shown in Table \@ref(tab:embeddings-flood-zone) as compared to Table 
\@ref(tab:relativities). In Section TODO, we will discuss techniques to visualize these embeddings.

Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type`.

|level                                       | embedding|
|:-------------------------------------------|---------:|
|2 to 4 unit residential buidling            |      6.69|
|Non-residential building                    |      7.16|
|Residential building with more than 4 units |      6.33|
|Single family residence                     |      5.43|

Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone`.

|level | embedding|level | embedding|level | embedding|level | embedding|level | embedding|
|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
|A     |      0.38|A09   |     -1.71|A18   |     -1.40|A99   |     -2.68|V     |     -0.41|
|A00   |     -0.35|A0B   |      3.85|A19   |     -1.70|AE    |     -4.46|V02   |      0.65|
|A01   |     -6.76|A10   |     -4.03|A20   |     -4.05|AH    |     -2.35|V03   |     -0.29|
|A02   |     -4.28|A11   |     -5.32|A21   |     -2.08|AHB   |     -1.71|V04   |     -1.15|
|A03   |     -5.93|A12   |     -3.23|A22   |     -2.11|AO    |     -6.07|V05   |     -0.50|
|A04   |     -7.82|A13   |      2.03|A23   |     -1.40|AOB   |     -4.56|V06   |     -1.92|
|A05   |     -3.42|A14   |     -5.72|A24   |      2.23|AR    |     -0.48|V07   |     -2.91|
|A06   |     -4.97|A15   |     -3.67|A25   |      0.28|B     |     -5.36|V08   |     -2.24|
|A07   |     -3.09|A16   |     -3.02|A27   |     -2.56|C     |     -4.47|V09   |     -0.75|
|A08   |     -4.69|A17   |     -0.37|A30   |      1.13|D     |     -0.76|V10   |     -2.05|
